---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# healthyR.data

<!-- badges: start -->
<!-- badges: end -->

The goal of the { healthyR.data } package is to provide a simple yet feature rich
administrative data-set allowing for the testing of functions inside of the 
{ healthyR } package. It can be used to test its functions or any function you create.

## Installation

NOT YET ON CRAN - You can install the released version of healthyR.data from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("healthyR.data")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("spsanderson/healthyR.data")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(healthyR.data)
## basic example code
```
